---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# beecalculator

<!-- badges: start -->
<!-- badges: end -->

The goal of beecalculator is to help beekeepers make accurate calculations for bee related subjects

## Installation

You can install the development version of beecalculator from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Thijmenvanbrenk/beecalculator")
```

## Calculators

This package contains 2 calculating functions:        
1. checking the mating flight details of your hive with *bee_mating_flight()*        

```{r bee mating flight}
library(beecalculator)
#> larvae_size is depended on how big the larvae in the swarm cell is: 1 = egg, 2 = small larvae, 3 = big larvae
bee_mating_flight(date = "27/04/2022", swarmcells = T, larvae_size = 3)

bee_mating_flight(date = "27/04/2022", swarmcells = F)
```
<br>        
2. calculating how much food is needed before winter with *bee_winterfood()*

```{r bee winter food}
#> all values are in amount of full frames
bee_winterfood(honey = 5, pollen = 2.5, bees = 11)

bee_winterfood(honey = 5, pollen = 1.5, bees = 16)
```


## kastkaart generators

there are 2 functions present that create and update the kastkaart:       
1. creating the kastkaart with *bee_kastkaart()*

```{r bee kastkaart}

bee_kastkaart(date = "27/04/2022", size =  6, name =  "Henkie", swarm = "No", mated = "Yes", export = TRUE)
knitr::kable(read.csv("Henkie_hive.csv"))

```
<br>        
2. updating the kastkaart with *bee_kastkaart_update()*

```{r}
bee_kastkaart_update(file = "Henkie_hive.csv", date =  "03/05/2022", location =  "Ochten", honey = 2, extra1 = "Extra checkup to illustrate function")
knitr::kable(read.csv("Henkie_hive.csv"))
```

