---
title: "bee_vignette"
author: "Thijmen van Brenk"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bee_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

In the beekeeping industry it is important to document the things you do inside of the hive, if you only have a few hive using a piece of paper could be enough. But whenever you have more than 4 hives you have to either leave the paper on the hive or you will lose track of which paper is from which hive. In this R package you can easily create a new hive card and update that same hive card every time you look into the hive.        
Calculating how much food is required before winter and how many days it takes before the queen goes on her mating flight can be done by hand but takes a while and is prone to mistakes. In this R package there are 2 functions that will calculate for you when the queen goes on her mating flight and how much you need to feed your hives before winter (using amounts that are normal for winters in the netherlands).

# installation

At this point you can only download `beecalculator` from Github:
```{r, warning=FALSE, message=FALSE, error=FALSE, results='hide'}
# install.packages("devtools")
devtools::install_github("Thijmenvanbrenk/beecalculator")
```

# functions

## Winter food calculator

The required inputs to calculate how much food is necessary before winter are `honey`, `pollen` and `bees`.        
The honey input calculates how much more honey is needed.       
The pollen input calculates how much more pollen frames are needed.       
The amount of bees in the hive can influence the necessary amount of honey required before winter.

```{r setup}
# Load the beecalculator library
library(beecalculator)
```

```{r, collapse = TRUE, comment = "#>"}
# the input amount is in full frames. so 2 frames that are half full of bees will become 1 full frame of bees for this function.
bee_winterfood(honey = 3.5, pollen = 2, bees = 16)
```

## mating flight calculator

The only required input is the date from when the old queen has been removed from the hive to start procedure.        
There is however the possiblity that there were already swarm cells present before removing the queen, this has some implications on the dates which is why there are 2 extra options for this.        
`larvae_size` is a prediction of how big the larvae is. it has 3 options:       
1 = the swarm cells only contain eggs.       
2 = the swarm cells only contain small larvae (1-3 days old).       
3 = the swarm cells only contain big larvae (4-6 days old).

```{r, collapse = TRUE, comment = "#>"}
# data has to be in format "dd/mm/yyyy"
# larvae_size has to be a number between 1 and 3. read explaination above.

# one example without swarm cells
bee_mating_flight(date = "27/04/2022")

# 2 examples with swarm cells
bee_mating_flight(date = "27/04/2022", swarmcells = T, larvae_size = 1)
bee_mating_flight(date = "27/04/2022", swarmcells = T, larvae_size = 3)
```
## setting up hive card 

A hive card gets created when you either make a split or when you catch a swarm hence why there are not that many option. required inputs are the `date`, `size`, `name` and `swarm`.       
date can be in any format.        
size needs to be in full frames.        
name needs to be a character string that defines the name of this hive.
swarm needs to be either "Yes" or "No"        
if you need to know the origin of the hive and if the queen is mated or not this can also be added.       
if you want to preview the hive card before using it export can stay false, if you want to export it into a csv file to build upon later switch it to export = TRUE.

```{r, collapse = TRUE, comment = "#>"}
bee_kastkaart(date = "27/04/2022", size =  6, name = "Truus", swarm = "No", origin = "F1 Bram", mated = "Yes", export = TRUE)
bee_kastkaart(date = "27/04/2022", size =  10, name = "Felix", swarm = "Yes")
```

To update the hive card the only required fields are `file`, `date` and `location`.       
file is required to find the csv file to build further upon.        
date to show which day you added a check up.        
location to know where the hive was at the moment of check up.        
all the other data is optional and only has to be filled in if thoroughly checked.        

```{r}
bee_kastkaart_update(file = "Truus_hive.csv", date = "01/05/2022", location = "Eldik", extra1 = "Checked if queen surived split")
bee_kastkaart_update(file = "Truus_hive.csv", date = "07/07/2022", location = "Lienden", size = 17, brood = 11, swarmcells = 2, honey = 12, extra1 = "Harvested honey")
knitr::kable(read.csv("Truus_hive.csv"))
```

# Available data

## Kastkaart

This package contains 1 dataframe called kastkaart. this datafile shows what a kastkaart looks like when it has been filled up with lots of check ups.

```{r, collapse = TRUE, comment = "#>"}
knitr::kable(beecalculator::kastkaart)
```

